\bfseries\LARGE\singlespacing{Transmission of respiratory viral infections with and without air cleaners in a Swiss school under non-pandemic conditions in 2023: A modeling study of epidemiological, environmental, and molecular data}

### 2023-10-03 doc/paper/manuscript.tex
Updates from Overleaf

\begin{figure}[!htpb]
    \centering
    \includegraphics{../../results/mol-data/descriptives.pdf}
    \caption{\textbf{Analysis of molecular data}. \textbf{(a)}~Number of positive saliva samples by virus. \textbf{(b)}~Number of positive saliva samples by study condition. \textbf{(c)}~Possible transmission chains within classes. Direction of transmission as arrows. Number of infections per day as dot sizes. Viruses: Influenza B (Flu B), rhinovirus (HRV), adenovirus (AdV), SARS-CoV-2 (CoV), metapneumovirus (MPV), parainfluenza virus (PIV).}
    \label{fig:molecular-descriptives}
\end{figure}

>>>>

\begin{figure}[!htpb]
    \centering
    \includegraphics{../../results/mol-data/descriptives.pdf}
    \caption{\textbf{Analysis of molecular data}. \textbf{(a,b)}~No. of positive saliva samples by virus and study condition. \textbf{(c)}~Daily no. of infections (1 to 3 as dot sizes) and possible transmission chains (arrows). Flu B: Influenza B, HRV: rhinovirus, AdV: adenovirus, CoV: SARS-CoV-2, MPV: metapneumovirus, PIV: parainfluenza virus.}
    \label{fig:molecular-descriptives}
\end{figure}
